### 2020-05-28 serial_guide.tex
done

% Created by tikzDevice version 0.12.3 on 2020-05-22 09:42:54
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+x_1$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,421.76) {$p$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,409.50) {Infector (reference cohort)};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,421.76) {$p+\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\sigma+x_2$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,544.35) {Intrinsic serial interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,470.79) {Intrinsic incubation period};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,495.31) {Intrinsic generation interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,519.83) {Intrinsic incubation period};
\definecolor{fillColor}{RGB}{255,255,255}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-x_1$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,216.78) {Infector};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,216.78) {Reference cohort};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-x_1+\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-x_1+\sigma+x_2$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,351.63) {Forward serial interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,278.07) {Backward incubation period};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,302.59) {Forward generation interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,327.11) {Forward incubation period};
\definecolor{fillColor}{RGB}{255,255,255}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-x_2$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-x_2-\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-x_2-\sigma+x_1$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 24.06) {Infectee};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 24.06) {Reference cohort};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,158.91) {Backward serial interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85, 85.35) {Backward incubation period};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (362.72,109.87) {Backward generation interval};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,134.39) {Forward incubation period};
\definecolor{fillColor}{RGB}{255,255,255}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-27 19:48:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,421.76) {$p+\tau_{\rm i1}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,421.76) {$p$};
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,409.50) {Infector (reference cohort)};
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,421.76) {$p+\tau_{\rm g}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,421.76) {$p+\tau_{\rm g}+\tau_{\rm i2}$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,544.35) {Intrinsic serial interval, $\tau_{\rm s} = (\tau_{\rm g} + \tau_{\rm i2}) - \tau_{\rm i1}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,470.79) {Intrinsic incubation period, $\tau_{\rm i1}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,495.31) {Intrinsic generation interval, $\tau_{\rm g}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,519.83) {Intrinsic incubation period, $\tau_{\rm i2}$};
\definecolor{fillColor}{RGB}{255,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,229.04) {$p-\tau_{\rm i1}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04,216.78) {Infector};
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16,216.78) {Reference cohort};
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,229.04) {$p-\tau_{\rm i1}+\tau_{\rm g}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41,229.04) {$p-\tau_{\rm i1}+\tau_{\rm g}+\tau_{\rm i2}$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,351.63) {Forward serial interval, $\tau_{\rm s} = (\tau_{\rm g} + \tau_{\rm i2}) - \tau_{\rm i1}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,278.07) {Backward incubation period, $\tau_{\rm i1}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,302.59) {Forward generation interval, $\tau_{\rm g}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85,327.11) {Forward incubation period, $\tau_{\rm i2}$};
\definecolor{fillColor}{RGB}{255,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 36.32) {$s-\tau_{\rm i2}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (121.04, 36.32) {$s-\tau_{\rm i2}-\tau_{\rm g}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (282.16, 36.32) {$s-\tau_{\rm i2}-\tau_{\rm g}+\tau_{\rm i1}$};

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29, 24.06) {Infectee};
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (604.41, 24.06) {Reference cohort};
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (443.29,158.91) {Backward serial interval, $\tau_{\rm s} = (\tau_{\rm g} + \tau_{\rm i2}) - \tau_{\rm i1}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (523.85, 85.35) {Backward incubation period, $\tau_{\rm i2}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (362.72,109.87) {Backward generation interval, $\tau_{\rm g}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (201.60,134.39) {Forward incubation period, $\tau_{\rm i1}$};
\definecolor{fillColor}{RGB}{255,0,0}
